\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-03 papers/jfp/6-implementations.tex
Update TODOs
Tweaks to S6

Our model of \Excel uses the \hs{restarting} scheduler and the
\hs{dirtyBitRebuilder}, see Fig.~\ref{fig-excel-implementation}. The persistent
build information \hs{ExcelInfo}~\hs{k} is a pair: (i) a map
\hs{k}~\hs{->}~\hs{Bool} associating a dirty bit with every key, and (ii) a
calc chain of type \hs{[@@k]} recorded in the previous build
(\S\ref{sec-background-excel}).

@@

Fig.~\ref{fig-cloud-implementations} shows our models of several cloud build
systems. \Bazel, \CloudBuild and \Cloud \Shake are based on constructive traces
(\S\ref{sec-constructive-traces}), whereas \Buck and \Nix use their deep
variant (\S\ref{sec-deep-constructive-traces}).

@@

Note that although both our model and \Bazel's actual implementation supports
dynamic dependencies, it is currently not possible to define new monadic build
rules in the language available to users. Instead, users have to rely on a
collection of predefined built-in rules, which cover many
important instances of dynamic dependencies.

By switching to the \hs{topological} scheduler, we obtain a model of
Microsoft's \CloudBuild~-- an applicative build system that combines
conventional scheduling of statically known directed acyclic graphs of
dependencies with constructive traces~\cite{esfahani2016cloudbuild}. Note that
we need to convert a monadic \hs{ctRebuilder} into an applicative one by
applying an adapter function \hs{adaptRebuilder}, which unwraps a given
\hs{Task}~\hs{Applicative} and wraps it into \hs{Task}~\hs{Monad}.

@@

\todo{AM}{Add implementation of \hs{dctRebuilder}?}

>>>>

Our model of \Excel uses the \hs{restarting} scheduler and the
\hs{dirtyBitRebuilder}, see Fig.~\ref{fig-excel-implementation}. The persistent
build information \hs{ExcelInfo}~\hs{k} is a pair of: (i) a map
\hs{k}~\hs{->}~\hs{Bool} associating a dirty bit with every key, and (ii) a
calc chain of type \hs{[@@k]} recorded from the previous build
(\S\ref{sec-background-excel}).

@@

Fig.~\ref{fig-cloud-implementations} shows our models of several cloud build
systems. \Bazel, \CloudBuild and \Cloud \Shake are based on constructive traces
(\S\ref{sec-constructive-traces}), whereas \Buck and \Nix use deep
constructive traces (\S\ref{sec-deep-constructive-traces}).

@@

Note that although both our model and \Bazel's actual implementation supports
dynamic dependencies, it is currently not possible to define new monadic build
rules in the language available to users. Instead, users have to rely on a
collection of predefined built-in rules, which cover many
common instances of dynamic dependencies.

By switching to the \hs{topological} scheduler, we obtain a model of
Microsoft's \CloudBuild~-- an applicative build system that combines
conventional scheduling of statically known directed acyclic graphs
with constructive traces~\cite{esfahani2016cloudbuild}. Note that
we need to convert a monadic \hs{ctRebuilder} into an applicative one by
applying an adapter function \hs{adaptRebuilder}, which unwraps a given
\hs{Task}~\hs{Applicative} and wraps it into \hs{Task}~\hs{Monad}.

@@

% \todo{AM}{Add implementation of \hs{dctRebuilder}?}
